Quality Criteria for SKOS Vocabularies

### 2012-03-20 criteria.tex
minor fixes in intro to 3

We identified an initial set of quality criteria for SKOS vocabularies by reviewing existing literature and manually examining existing vocabularies. We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions. Based on the responses we received, we then selected a subset of these criteria and formalized them into computable \textbf{quality checking functions}. Each of these functions operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:

@@

In the following, we explain the origins and design rationale for each quality criterion and describe how we implemented the corresponding quality checking function. For better readability we provide semi-formal definitions only where necessary and refer to the online documentation or the implementation source code for further details. We also categorized the identified quality criteria into \emph{labeling and documentation criteria}, \emph{structural criteria}, \emph{Linked Data specific criteria}, and \emph{other criteria}.

>>>>

We identified an initial set of quality criteria for SKOS vocabularies by reviewing existing literature and manually examining existing vocabularies. We published our findings online\footnote{\url{https://github.com/cmader/qSKOS/wiki/Quality-Criteria-for-SKOS-Vocabularies}} and requested feedback from experts via public mailing list and informal face to face discussions. Based on the responses we received, we then selected a subset of these criteria and formalized them into computable \textbf{quality checking functions}. Each function operates on a SKOS vocabulary, which we define, for the purpose of this work, as follows:

@@

In the following, we explain the origins and design rationale for each quality criterion and describe how we implemented the corresponding quality checking function. For better readability we provide semi-formal definitions only where necessary and refer to the online documentation or the implementation source code for further details. We also categorized the identified quality criteria into \emph{Labeling and Documentation Criteria}, \emph{Structural Criteria}, \emph{Linked Data Specific Criteria}, and \emph{Other Criteria}.

### 2012-03-20 introduction.tex
minor fixes in intro to 3

	\item We identified \todo{CM}{XX} \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{filtering functions} that identify possibly affected resources in a given SKOS vocabulary.

>>>>

	\item We identified \todo{CM}{XX} \textbf{quality criteria} for SKOS vocabularies by examining existing guidelines and formalized them into computable \textbf{quality checking functions} that identify possibly affected resources in a given SKOS vocabulary.
